---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# packagedapis

<!-- badges: start -->
[![R-CMD-check](https://github.com/edgararuiz/packagedapis/workflows/R-CMD-check/badge.svg)](https://github.com/edgararuiz/packagedapis/actions)
<!-- badges: end -->

This package explores the mechanics of managing APIs within an R package.  The idea is to separate the functions and the API endpoint code. This will allow to also test the functions and the endpoints independently.  The idea is for the R package test and checks will test the endpoints as part of the verification process. 

## Please clone, don't install

This package is meant to be an example for those who want to develop a package to maintain their APIs.  The best way to take advantage of it is to clone the repo, and then try running the tests and checks locally.  

## Package structure

```{r, eval = FALSE, include = FALSE}
fs::dir_tree()
```

The major pieces of the structure are presented in the file tree below.  To make it more concise, an explanation for each are in-line for each piece:

```
        Folder/File                                            Explanation
--------------------------   -------------------------------------------------------------------------
├── R
│   ├── common.R             Functions that the API actually executes. They need to be exported.
│   └── test-api-utils.R     Functions that enable the test of the actual API endpoints
├── inst
│   └── api1.R               The actual plumber API.  They call functions from this package.
└── tests
    ├── testthat
    │   ├── test-api1.R      Runs API in a new R session, and performs the tests against running API
    │   └── test-common.R    Tests functions in common.R script
```


